\Large {\bf rt1d: Documentation}

### 2012-04-24 doc/manual/rt1d_manual.tex
Added wiki/Home.wiki
Added documentation PDF.

%%% Beginning of Document
\begin{document}
\author{Jordan Mirocha}	
\title{\Large {\bf rt1d: User's Manual}}
\date{Last Updated: \today}
\maketitle

@@

@@

%%%
%% Test Problems
%%%
\section{Test Problems}
In this section we focus on test problems 1-3 of the Radiative Transfer Comparison Project \citep[hereafter RT06;][]{Iliev2006}.

@@

\begin{figure*}[htbp!]
\begin{center}
\includegraphics[width=0.98\textwidth]{figures/rt06_0.eps}
\caption{Convergence test for RT06 \#1.}
\label{fig:RT06_1}
\end{center}
\end{figure*}

@@

>>>>

%%% Beginning of Document
\begin{document}
\author{Jordan Mirocha}	
\title{\Large {\bf rt1d: Documentation}}
\date{Last Updated: \today}
\maketitle

@@

\item [\texttt{ProblemType = 0}] Single-zone.

@@

%%%
%% Test Problems
%%%
\section{Test Problems}
In this section we focus on test problems 0-3 of the Radiative Transfer Comparison Project \citep[hereafter RT06;][]{Iliev2006}.

@@

\begin{figure*}[htbp!]
\begin{center}
\includegraphics[width=0.98\textwidth]{figures/rt06_0.eps}
\caption{Single-zone ionization, heating, and cooling RT06 \#0.}
\label{fig:RT06_0}
\end{center}
\end{figure*}

@@

%%%
%% Advanced usage
%%%
\section{Advanced Usage}
